\section{Beez is given a choice}
\textbf{\LARGE Dramatis Personae}
\begin{multicols}{2}


\subsubsection{Military officers}
Captain Gregory H. Stonesworn,\par who gives what kindness he can. \newline
Lieutenant Dorian Fenwick,\par who takes any offense that is offered.

\subsubsection{A visiting delegation}
The dragonborn Mesheshi,\par The Breath of the Dragon. \newline
The human Kasdiel,\par assistant, friend, and companion. \newline

\subsubsection{A tiefling on the road}
Goldie, an Erudite of the Arcanum


\subsubsection{The Landslide}
Brukzhul, alias ``John Smith.'' \newline
Alotel, a high elf and John's second. \newline
Imrodel, a wood elf scout. \newline
Eagletamer, a goliath sapper. \newline
Fari, a hill dwarf, brash but practical. \newline
Quinn, a half-elf, cheerful and dewy-eyed. \newline

\subsubsection{The Crimson Strand}
Subcaptain Donavan Grey,\par Fenwick's terrier n\'ee brigand leader. \newline
Several others, whose names you never learned.

\subsubsection{Mentioned, but not present}
Lord-Baron Ezekiel Fenwick,\par for whom you previously fought \newline
Ayanum, ``The Silver Dragon,''\par benevolent ruler of the Dragonlands \newline
The Irongrip Dwarves,\par isolationist clans beneath Bilnulbar

\subsubsection{Locations}
Bilnulbar, a mountain chain to the north  \newline
Thornwold, capital of the Thornic Empire
\end{multicols}
\noindent
\hrulefill

\subsection*{Characters not noted elsewhere}

Gregory Stonesworn is a 80 years old male human soldier.
He has short, straight, black hair and brown eyes.
He has rugged red skin.
He stands 157cm (5'1") tall and has a round build.
He has an oval face with a short, neat beard.
He can't feel pain.
He discretely worships Selune, Goddess of the moon, stars, navigation, prophecy, questers, lycanthropes. (Neutral Good)
He is very empathic towards others.
He is very generous.
He likes finding direct solutions to problems.
\textbf{Voice: lifted, direct, gentle.}

Dorian Fenwick is a 26 years old male human soldier.
He has long, curled, auburn hair and brown eyes.
He has soft chocolate skin.
He stands 162cm (5'3") tall and has a lean build.
He has an edgy, cute face.
He discretely worships the demon prince Yeenoghu, Demon lord of gnolls. (Chaotic Evil)
He is very greedy.
He never surrenders.
He gets very mad at any semblance of an insult.
Dorian is the first son of your former lord baron.
He is generally a fop, but is well trained and of strategic mind.
\textbf{Voice: Sub-nasal, petulant, impetuous.}

\hrulefill
\clearpage

\begin{multicols}{2}
\subsection{Traveling to the Western Front}
  \begin{aloud}
  You are driving one of many supply wagons in a long train on the way to the western front.
  Your regiment, and consequently the squad you lead, has been transferred from your lord baron
    Fenwick to serve among the Imperial Forces.
  Not a promotion per se, but a step sideways.
  Now you fight at the whim of the Empress rather than the whim of a local lord.
  Here's to the new boss, same as the old boss.

  Your wagon, along with the two wagons behind you, contain your squad, the Landslide, as you
    bring up the rear of the supply train.
  It's the mid/late spring, but blessedly dry.
  The weather is as good as you could hope for, when you have to sit behind a team of horses,
    trundling along slower than you would walk.

  You began your journey last week.
  It was four days from your previous post to the western garrison.
  You left the garrison this morning, and it'll be two days more travel before you arrive at the
    forward camp.
  \end{aloud}

Call for a DC 20 Wisdom (Vehicle: Land) check.
The card trundles, wobbles, and bumps.

Ask if Beez knows his geography.
If so\dots

  \begin{aloud}
  To the west lies the Legion of Ayanum, but nearly everyone in calls it the Horde.
  From the rumor mill, you've heard that they're generally xenophobes and have a very magic-focused
    culture and political system.
  You've heard that the country is ruled by a lich, and you've heard that it's ruled by a dragon,
    and you've heard that it's ruled by an elected parliament.
  You know, the rumor mill.

  They've been historically peaceful, which makes the prospect of conflict with them a bit of a
    wildcard.

  \end{aloud}

Ask if Beez would keep an ear in politics.
If so\dots

  \begin{aloud}
  About a year ago, they sent an emissary to the capital.
  They met with the Emperess and her council.
  Word never got out what they talked about, but the group left unhappy.
  Ever since then the military has been shoring up it's western front.
  You've heard that political channels are still open, but it's clear that things in the west are
    headed south, as it were.
  \end{aloud}

Ask if Beez is doing anything in particular while he's riding along.
Ask if he would be alone or if one of the other Landslide would be riding with him.

Take a moment to describe the rest of the crew.
Eagletamer is walking, since the goliath would hardly fit in a cart.
Fari and Quinn love to banter and are riding together in another cart.
Alotel and Imrodel are riding in a companionable silence.

  \begin{aloud}
  Up ahead, you see a Tiefling off to the side of the road,
    walking so leisurely that your wagon is actually catchup up on them.
  They have their thumb out in the inter-universal symbol of the hitchhiker.
  Most humans are jumpy around teiflings, and as a result, tieflings more than any other race tend
    to wear nondescript, baggy robes and hooded cloaks to hide their distinguishing features.
  But this one is just hanging out, brown-orange skin the color of actual copper,
    high-held head sporting small ibex-like horns,
    hair the dark blue of veins pulled back into a tail,
    and a pointed tail swishing as they walk.

  A few wagons ahead, someone upturns a pitcher of something at them.
  They dodge back in time, and while you can't hear the words that are exchanged, it's pretty clear
    the meaning.
  The tiefling tosses their pack onto the ground, taps their chest and holds their arms out in
    an invitation to fight.
  The other wagon keeps moving.

  After the wagon's moved on, the tiefling picks up their pack and, noticing the muck, deflates
    a bit.
  She turns around, and you're close enough now that she catches your eye, looking at you with
    those solid-color tiefling eyes, hers silver.
  She smiles hopelessly, raises her eyebrows, and sticks out her thumb.
  \end{aloud}

DC 20 Wisdom (Vehicle, Land) check.
Something feels off.

Shoot the shit for a while.

Goldie (get it?).
Raven necklace.
She will be coy about why she's traveling west.
``An underling'' and/or ``a messenger.''

DC 15 Vehicle (Land, Wisdom) check.
Advantage if passed either the previous two.

Throw a wheel.

DC 25 to be fine.

On fail, DC 20 to break down in the trail.

On fail, DC 15 to avoid capsizing.

On fail, DC 10 to avoid crippling one of the horses.

Ad lib fallout.
It's getting late and you're still more than a day out from the forward camp, but you'll become
  separated from the main body of the train if you don't fix this quickly.
That may not be possible on a 15/10 failure.

Goldie will help in any case, but will be hesitant to use magic in front of the Landslide.
On anything other than a 25 success, Goldie takes off.
``No offense, but neither of us needs me here when your officer gets here.
See you around, big guy.''

If he brings it up, she'll magic it fixed quickly on a DC 20-success.

She gives him a silver for the lift.

\subsection{A Job for an Auxiliary Squad}

Life is uneventful after arriving at the forward camp.
Since you're arriving late, you claim space on the outskirts,
  which (asking here) suits you just fine, right?

Goldie visits once in a while.
She's still vague about what it is she's doing at a forward warcamp,
  but you've seen her speaking with officers on occasion.

Mostly, it's typical army camp bullshit -- hurry up and wait.
You haven't had any official orders, and as an auxiliary sub-captain, you decide how your squad
  spends your time.
Are there any particular preparations you and the Landslide make?
Are you essentially on shore leave, allowing your squad to catch some R\&R?
Alotel will probably spend the whole time sharpening and practicing with her weapons if left to
  her own devices.

Play out whatever Al says.

\hlinefill

It's early evening, maybe ten days after you've arrived.
What are you doing?
Where are the rest of the Landslide?

While you're doing that, Goldie arrives.
``Come on.
  Your captain wants to see you.''
If asked how she knows, a runner will appear delivering the same message.

It's a bit of a walk to the captain's tent in the center of camp.

The two of you arrive.
Donovan Grey is leaning lazily against one of the tent's thick posts.

Donovan is the subcaptain of the Crimson Strand, another auxiliary squad.
Rumor is that the Strand was a group of bandits, then mercenaries.
They were a favorite of Dorian Fenwick, your former lord-baron's first-son.
After some political maneuvering, Dorian was installed in your regiment as Lieutenant,
  and the call from the Empire for your regiment's service shocked them both.
The lord-baron practically pressed the Crimson Strand into service at that point, in an effort to
  keep his son out of harm's way.
You have crossed paths with Donovan some few times, and while he is crass, brutish, and
  cares little for anyone beyond himself, you've found him to be honest and no more hostile to you
  on account of your heritage than he is to anyone else on account of them not being him.

Seeing you approach, he shrugs himself to standing, not at military attention but acknowledging.
He scratches the stubble on his chin, then the stubble on the back of his head, spits,
  and nods to you.
``John.''

Out of curiosity, where do you position yourself?

Chat with Donavan.
``You makin' deals with demons now?''
Chuckle at own bad joke.

``Devil.
  You make a deal with a devil.
  A devil is cruel and clever, but you can deal with them.
  A \emph{demon} is just rage and brutality, death and destruction.''
She grins a feral grin.

You hear voices arguing inside.

Roll Perception.

20
``Surely there is \emph{someone} more\dots suitable.''
``I've made my decision, Fenwick.''

18
``My Crimson Strands, perhaps.
  They would be much more\dots presentable.''
``That will be all, Lieutenant.''

15 (probably beat by his passive?)
``They cut quite the figure in their parade uniforms, if I say.
  Much more befitting a --''
``You are dismissed, Fenwick.
  Speak another word beyond 'sir' and I'll have you whipped.''

Lieutenant Fenwick, the prick, storms out of the tent.
Seeing you, he draws up short.
He spits on the ground.
Then seeing Goldie, he sneers and can't seem to decide which of you he despises more.
``Come along, Donovan!''

``John.''

Enter the tent.

``Subcaptain Smith, thank you.
  Ahh, and I see our esteemed guest with with you.
  That will save me some time then.''
He stands, beckoning you to a table with a map of the surrounding area.

``Tomorrow morning, you will gather your squad and travel northeast-by-east,
    following the open stretch between the woodland and the mountain.
  Our Erudite guest of the Arcanum will join you.
  Twenty to thirty miles form here, the woodland will dips southward before curving north to meet
    the mountain.
  In the glenn there, you will meet the emissary from the Legion of Ayanum.
  You will escort them and any delegation with them here.

``It's a day's ride in either direction, perhaps more if they slow your return.
  When you arrive, bring them here directly.
  We might yet be able to avoid a war, and I am eager to hear what they have to say.
  [beat]
  Are your orders understood?''

``Very good.
  Erudite, please give us the room.''
As she leaves, ``At ease, subcaptain.''

He walks to a corner with pulls from a chest a bottle of whiskey and two glasses, holding them
  questioningly.
Needs a drink after any interaction with Fenwick.
``In truth and on confidence\ldots What do you think of that man?''
Let Al make fun of him.
``Yes, he's all that and more.
  But\ldots are there lines he would not cross?
  Or, if given a direct command, would you believe those lives under him to be forfeit, a question
    only of when?''

Mull it over.

``Well, I'm sure you have preparations to make.
  I will see you in a few days, subcaptain.
  Safe travels.''

Ask Al about preparations being made, wagon or just horses, any extras?

\subsection{Escort quests are the worst}

Travel is uneventful.

TODO: Describe the Meshishi upon meeting.
The far woods are wrapped in mist.

``What must be done to prevent war between our people?''

  \begin{aloud}
  ``You misunderstand.
    We do not wish for there to be conflict between us.
    We do not wish for there to be \emph{contact} between us.
    This country and its people are of a disease,
      and if it cannot be cut out, we must not allow it to spread.''
    The humans scowl, while the dragonborn's aide whispers something to him.
  ``I apologize.
    It appears I neglect some of your language's nuance.
    I speak neither metaphor nor insult.
    Our augers have forseen a plague borne from your empire, a disease of blood and of mind.
    We will not allow the pathogen within our borders.
    Your leaders refused our aid in rooting it out, and in respecting your nation's sovereignty,
      we are left at an impasse.''

  ``So what does all of this have to do with you massing your army at the border?''
     asks the Captain.
  ``As I said, you misunderstand.
    You see not an force of invasion, but one of defense.
    Any living thing that approaches the Dragonlands will be swiftly and summarily executed.
    Our sorcerers will scorch their bodies and the earth beneath them.
    Our archers will kill every buzzard that would eat their flesh.
    Beginning now, \emph{nothing} [beat] enters the Dragonlands.''

    He speaks the next words quickly and reverently, as if reciting a prayer.
  ``My words are carried on the breath of the Gold Dragon,
      whose wisdom is boundless, whose word is law, and whose will is absolute.''
  \end{aloud}

If all doesn't ask the question, then the captain will offer respite for the evening and
  those that escorted you here will see to your safe return.

Meshishi looks confused.
``Was I unclear?
  No living thing enters the Dragonlands, not even me.
  The risk is too great.
  However, I will neither impose upon your hospitality.
  Arrangements have been made with the Dwarves in the mountains to the north.''

``Then subcaptain Smith and his men will see you to their borders in the morning.''

\subsection{More escort quests?!}

Travel again is uneventful.
You reach the border, and in a narrow mountain pass, the Dwarves have established a checkpoint.
What's your marching order?

\subsection{Combat}

This one's going to be a cluster-cuss.

For Donavan, use the Thug.

For the rest of his merry band, use Bandit.

Alotel: Veteran.

Ask Al who in the troupe would be sword-and-board.
Use Guard for them, Bandit otherwise.

Use Scout for Imrodel.

Use Acolyte for Meshishi and Kasdiel both, but they are cowards.

Use Mage for Goldie, limit to level 1 and 2 spells.
Add Chill Touch cantrip, Hex and Witch Bolt L1, Shatter and Darkness L2

\subsection{Awoken in Death}

A woman, a cloak, a raven.

It cocks its head at you, questioning, considering, offering.

\subsection{You awake.}

Carnage everywhere.
You are the only survivor.

\subsection{Scene: A healer is given a choice}

Promotion to Warrant Sergent, conditional on reporting to Celadir's Bastion.

\end{multicols}
