\section{A night in Burreldale}

\textbf{\LARGE Dramatis Personae}
\subsubsection*{In the moss}
\hyperref[npc:nat]{Nathaniel Silverson, the friendliest of allies.} \newline
\hyperref[npc:rosaline]{Rosaline, a guardian.} \newline
\hyperref[npc:sera]{Sera, whose name is good as any.} \newline
Various and sundry merchants of good cheer. \newline



\begin{aloud}
	First, we should retcon Gran's goodbye, but not much.
	But she wouldn't have sent you off blind.
	So in that last scene, where you returned her tangle and she gave you a red ribbon (which you put... in your beard?)
	She'd look into your eye and see the spirit you are hosting.
	She nods sadly.
	``You're going on an adventure, Jo.
	The... thing inside you...
	You have to keep is safe and carry it to a place far away from here.
	But the cards told me that you'll come back.''
	She nods, seeming to be trying to convince herself.
	
	She'll tell him that Nat will be in town, waiting.
\end{aloud}

\begin{aloud}
    You know, a letter arrived today.
\end{aloud}


\begin{multicols}{2}
  \subsection{On the road to what may be}
  \begin{aloud}
    You and Nat fall into a comfortable rhythm over days of travel.
    He fills the hours with song and stories, some of which you've heard but most of which are new to you.
    Your earnestness and enjoyment makes you the perfect audience in his eyes.

    Most nights, you sleep out in the wild.
    Every once in a while, you come across villages where Nat will spend a day plying his trade.
    Rarely, you cross paths with other traders, either in towns or on the roads.
	In these instances, you stop and trade news.
	
	After once such stop, Nat seems very excited.
	He mentions that you'll be making a detour off your intended route, but it will only add a few days.
	And since you don't really know where you're going, it's all the same to you.
  \end{aloud}

  \vfill\null
  \columnbreak

\subsection{A night in Burreldale}
  \begin{aloud}
    It's perhaps a month after you've left Shortspur.
    Nat is getting visibly excited.
    After turning down a fork in the road, he asks you to take the reins so he can ``get ready.''
    He slips into the back of the wagon.
    
    A few minutes later, just before a turn in the road, three guards stand near the road.
    Two are a bit farther back, sharing a roll-up.

    The nearer smiles warmly, approaching the cart.
    She is a half-elf with a wiry build and olive skin, seemingly perfectly at ease in her leather armor.
    Blonde hair is kept in a tight bun, and a cudgel and sword both hang hat her hip.
    She waves one hand, the other resting on the butt of her cudgel.
  \end{aloud}

  ``Ho there!
    You lost, friend?
    The road past Thornwold was the right at that last fork.
    Unless that's where you've come from, in which case you would've meant to take the fork on the left.
    But this here dead-ends in a clearing, and it's a prive night tonight, 'm 'fraid.''

  See if Jo can work his way into or out of trouble here.
  Maybe recognize the cart if Jo mentiones it or BlueMan.
  Rosaline approaches to 5-10ft from the cart.
  
  Note Jo's response, if it's suitable as the 'right' one.
  If so, rustling in the back makes Rosa concerned.
  ``Anyone with you in there?''
  
  \begin{aloud}
    The Nat that emerges is barely recognizable as the one who went in.
    The wide floppy hat has been replaced by a tricorn hat, his simple travel clothes with fine breeches.
    As he steps out, he is fussing to get his bright blue ascot under a puffy white shirt.
  \end{aloud}

  Rosaline smoothly flicks her cudgle through the mud, lobbing a glob at Nat.
  
  Oh, look what you've done.''  ``No harm in looking filthy as every woman here knows you are, you old scroat.''  Rosaline grins.
  
  You out here all night, then?''  ``I'll be in after sundown.  Plenty of time to find some trouble.''
  
  Come find me then, yeah?''  Nat goes to pick up the reins, but Rosaline's hand grabs his wrist.
  
  You know the rules.  It's your cart, so you have to say the words.''
  
  Ehrm right.  Umm... feed me your line again?''
  
  Either do the callback to the right line, or feel around for a ''right'' passphrase.  Otherwise, ``A private party is the best place for a public nuisance!''
\vfill\null\columnbreak
\subsection{We all forgot our troubles}
  \begin{aloud}
  All around the edge of the clearing, dozens of other merchant carts have been parked.

  A tall pole in the center, ribbons streaming from it, with men and women dancing around.

  Smaller campfires scattered about.
  The scents of various cookpots hit you from all directions, making your mouth water.

  Many clumps of people, engaged in various activities.
  In one clump, half-dressed men are wrestling, to the cheers of on-lookers.
  In another, a rider looks like he's going to do some tricks, but someone slaps his horse's haunch, causing it to jolt the rider into a stack of dirty cookery.
  In the distance, a holy-man is having a quiet but tense argument with a bookish looking man, who doesn't seem to be aware that the fire behind him flares in time with his gesticulations.

  You realize this is the first time you've seen a group of people with fewer humans than other races.
  There are a great many dwarves, halflings, and gnomes present, and more than the average number of elves, half-elves, and half-orcs.

  \end{aloud}

\end{multicols}