\section{Another day, another drink}
\begin{multicols}{2}
  \begin{aloud}
    It's early morning, mid-spring, and you're sitting at a table at the Last Shot.
    It's the end of your week back ``on shore.''
    The final preparations are being made, and you'll cross back into the wilds before lunch.

    Whitney, is recounting a story he'd heard this week,
      the \emph{real} story of how the some great wizard Merlin formed the Gash during the
      Bleak War hundreds of years ago.
    He looks like a merchant;
     everything about him is round.
    He has long curled hair, healthy bronze skin, and a gigantic braided beard.

    Your leader, Gluri Frosthand, is seated at the bar.
    Gluri has been in this town for as long as it's been worth being here.
    The dwarf is shaved bald, and his brown skin is perpetually sunburned a hint of red.
    He's got the ugliest goatee you've ever seen, and he love it.
    His right hand is missing the last two fingers.

    He's chatting up the bartender, Skril, and making final supply requests.
    She's one of those human contradictions.
    A glance at her, and you'd think she's the meanest bitch you'd ever met.
    Dark hair is shaved to stubble, her arms are crisscrossed with combat scars.
    She brooks no nonsense in her bar, and the way the town has been going, it's threatened to see
      plenty of nonsense these days.
    But you've come here long enough to know she also has an easy laugh and a kind heart.

    The other two members of your crew have gone ahead to the Bridge to talk to the guards there.
    The bar is otherwise empty, save for two dedicated drunks each at separate tables.

  \end{aloud}

  What is Spacky doing?
  Anything special to get ready for your trips out to the Wastes?

  \begin{aloud}
    The bar door opens, admitting the town's contrasting populations in a backlit frame.
    The Celedonian enters first, tall and regal in his simple but well-made robe and cloak.
    The elf is made entirely of straight lines.
    His goatee suits him well, his thin, dark staff of office thumps quietly as he walks.
    He holds the door open.

    Blind Carolyn's walking stick \emph{thwacks} the frame of the door and she fumbles her way in.
    Everything about the human woman is worn.
    Her white dress is frayed and threadbare.
    She moves with a slow, tired pace.
    Her eyes are milky white, with burn scars radiating outward.

    The Celedonian goes to the bar with Gluri and Skril.
    Blind Carolyn squints into the room, and begins feeling her way to your table.
  \end{aloud}

  [Pause to see if Spacky responds.]

  ``The light of \Enyhito\ shine upon you, Mister Bolbec,'' she greets.
  ``Spacky.'' She nods.
  ``May I join you boys?''

  [See how it plays out.
   Carolyn could prompt Whit to keep going with his story.
   Play this part by ear.
   Stew is eventually delivered.
   A pleasant, quiet meal passes.
   Gluri says "Let's go."
   Carolyn stops Spacky as he is getting up.
   ``I\ldots'' she falters.
   ``I've seen dark times ahead.
     For everyone, but particularly for you.
     Remember there are we who would help you find the light again, if you lose it.''
  End with ``\Enyhito keep you safe.''
  ]

  \subsection{A good week, Wasted}
  Gluri, Whitney, and you are heading to the Bridge.
  Gluri hands you a sheet of parchment.
  ``Here's what's valuable.
    What do you think?''

  [Let Alex assess.
   Maybe some Nature rolls to see if he thinks he's confident he could track some down.
   More to assess the danger level.]

  \newpage
  \begin{itemize}
    \item[] Meat
    \begin{itemize}
      \item Elk
      \item \underline{Axe Beak}
    \end{itemize}
    \item[]
    \item[] Skins, teeth
    \begin{itemize}
      \item Bear
      \item Hyena
      \item Wolf
      \item \underline{Dire Wolf}
      \item \underline{Worg}
      \item \underline{\underline{{Basilisk acid sacs}}}
    \end{itemize}
    \item[]
    \item[] Intact
    \begin{itemize}
      \item Blood Hawk
      \item Blink Dog
      \item Cockatrice
      \item Stirge
    \end{itemize}
    \item[]
    \item[] Standard Bounty
    \begin{itemize}
      \item Goblin (thumbs)
      \item Orc (thumbs)
      \item Harpy (feet)
      \item Gnoll (thumbs)
    \end{itemize}
  \end{itemize}

  \newpage

  As you approach the bridge, you see Ogden and Lilith, the frontman and the muscle
    of your merry band.
  [Read their description blocks.]

  Entering the wastes isn't something you ever get used to.
  Actually, the Wastes are fine.
  It's crossing the Gash that's unsettling.

  Wind whips past you, rushing up from the depths of the ravine.
  Today, it is brutally hot and smells acidic, but only a week ago it was rot carried on
    a freezing wind.
  The bridge itself is centuries old, a dozen yards wide and two thousand span across.
  And from here, you set into the Wastes.

  \subsection{Out and back, again}

  You track your quarry.
  Gluri has a magic box that keeps things from rotting, and seems to hold a lot more than it ought.

  Play it by ear.

  Scout up to find whatever you're looking for.

  Maybe when you get back, Ogden is gone.
  ``Went to forage.
    Should be back by now.''
  Or he just comes back with a dead Basilisk.

  Spacky, prepare it!

  Survival check, because.

  Pull its inards, paying special attention it its many acid sacs, since that's where the money is.
  Head's in good condition, so it can get lopped by itself.

  While it's cooking, Lilith scolds Ogden for going after that thing alone.
  He waves it off, but Gluri adds the weight of command to it.
  ``I'm happy with how it turned out, boy, but you could've done it a hell of a lot better.
    You did well, but you did it wrong.''

  [Talk about the stomachs.]
  []
  \end{multicols}
