*"Wh... Why are you doing this?"
 The slurred voice quavered from the gutter.
 None of us had noticed the wretch, unmoving, his body pooling the filth running downhill.
 Or perhaps some had, but assumed that the fires would take him, if that was her will.

 He stood slowly, convulsing, scar-strewn arms twitching over an exposed, emaciated stomach.
 A thunder-scratch addict, then.
 I remembered the throbbing that drug once brought me, wave after wave of ecstasy crashing into me
  as I lay in a gutter indistinguishable from his.

"Leigáz wills it, friend."
 I smiled at him as his eyes searched mine, the smile a father gives a child.
 He stared uncomprehending, horrified as the fires began to burn the building in earnest.
 He backed away, tripping to sprawl backwards over the gutter he occupied only moments ago.

"Hush, friend.
 Fear not.
 The fire does not harm the faithful."
 I knelt down, extending my charred hand from my robe and placing it in the tangled nest of scars
  in crook of the man's elbow.
 He flinched, just as I had those years ago.

"Light of Phlegethos," I intoned, "burn away this man's impurity.
 Show him your warmth.
 Instill in him your burning passion."
 My blackened hand blurred as it heated over the span of two heartbeats,
  before the flames took hold once again.
 I watched as the man's eyes flickered through the emotions.
 The fear of the fire and repulsion at the smell of burning flesh, hair, and filth fled quickly,
  replaced by surprise and confusion that he remained unharmed.

 Then I felt her touch, the sweet release as Leigáz herself entered my mind and owned my flesh.
 I was adrift in her, every concern eradicated by the river of fire that blazed me.
 I could see that he felt her too.
 His eyes grew wide, his head falling back, and a slow moan falling from an agape mouth.

"Your mortal dalliances are so quaint," she spoke through my mouth.
"But Abriymoch has stood for eternities.
 We have so much more to offer you."
 The man's response was emphatic, wordless mumbling.
 His slid slowly back into his gutter, eyes rolling back into his head.

By the morning, the entire eight ward of Thornholm would be ash, the worst of our opposition burned away.
By midday, this man would awaken with a singular focus, to feel again what he had briefly tasted.
By evening, he would either find us and join our order,
 or he would lose whatever is left of his mind as the cold invaded where her warmth had been.

I stood.
There was much more to do through the ward tonight.
Other buildings to burn, other wayward souls to enlighten, several deaths to ensure.
All as she wills it.





## Leigáz (/'lāgaz/), the Sweet Release
Daughter of Fierna, Light of Phlegethos

**Domains:** Death, Grave, Light, Domination, Fire, Hunger, Lust

Dogma:
The "revealed truths" that only the clergy know and rules they must follow

Tenets:
* Mark

## Allies of the Faith:

*Fierna and Belial.*
As the

spawned
Friends of the faith

Enemies of the Faith:
*Enyhítő*

Clergy and Temples: The priesthood and its variants and the colors and symbols used

Holidays and Festivals: The sacred and secular celebrations

Champions and Avatars: Mortal heroes and Divine incarnations

Known Sects/Cults: Any deviant interpretation of the true faith

Anthing Else You Want: Anything not covered here that you would like to include, like restricted weapons or armors, boons, granted powers, whatever.



############

## Her Divine Radiance, Enyhítő (/ɛɲ'hētü/)
The Guiding Light, The Halo ,

**Domains:** Life, Light, Protection, Solidarity, Community, Fire

