\section{Nathaniel Silverson}\label{npc:nat}
\quad\enspace{\small%
\textbf{\textit{Human Male, lawful neutral}} \par
\textbf{Commonly known as:} Nat \par
\textbf{NPC Voice:} Friendly, easy to laugh.  Think Jerome from Locke Lamora.%
}

\smallskip

\begin{aloud}
  A fair-skinned human male trader in his mid 20s.
  He wears a lightning-blue askot, a wide floppy hat atop short, curly hair, and otherwise simple travel fare.
  He tends towards chatter, which is not unpleasant given his decent skill as a story-teller and orator.
  
  His wagon is sturdy, drawn by a duo of draft horses.
  Both animals are impressively large.
  One has chestnut hair, the other patches black and white not unlike a cow.
  The exterior of the wagon simple,  but what space exists inside besides crates of wares is brightly colored in fabric and pillows.
  Several items hang in the interior near the front of the cart:
   a solid iron cage, an insense censer, a windchime made of jagged crystals, and two heavy lanters, spilling their light ahead of the wagon.
\end{aloud}

\dmonly{
Yeras ago, Nat's is a merchant's apprentice suddenly left in charge of the wagon after he
  and his master driven into the Ragged Witch's territory fleeing a pair of dire wolves.
His master was left to Meryl's ministrations, and Nat was sent away under the witch's geas to
  offer transport eastward anyone bearing her marker.
The gaes now expired, he serves the Meryl and the Raven Queen of his own will.

Nat's father was a bard of some renown.
While not infused with the same magical qualities, Nat has a fair baritone in his own right.

Nat can create decent forgeries for travel documents.
}


\section{Rosaline Mowbray}\label{npc:rosaline}
\begin{aloud}
	A half-elf with a wiry build and olive skin, seemingly perfectly at ease in her leather armor.
	Blonde hair is kept in a tight bun, and a cudgel and sword both are kept at her him.
	One hand waves as she speaks, the other resting on the butt of one of her weapons.
\end{aloud}

\section{Sera}\label{npc:sera}

\begin{aloud}
    A person, wrapped from head to toe in cloth.
    Dark goggles peer at you from over a linen full hood.
    Functional but loose clothes in brown and greys, with thin black gloves.
\end{aloud}

