\todo{Most of this is WIP, no longer consistent with the direction the plot has gone.}
\section{Ogden and Goldie}\label{sec:ogdenAndGoldie}
\headeritem{Also known as}{The Warrior and the Waif}

Ogden and Goldie are an adventuring duo, non-romantic couple that frequently crosses paths with
The Group.
Their path often intersects with The Group's between adventures, as they have gone on their own
adventures in the meantime.
Ogden and Goldie will perhaps pick up the adventures that The Group turns down, progressing
critical plot points in tandem.

They are almost comical in their night-and-day contrast to each other, sharing only that they are
both absurdly gorgeous, both favor studded leather armor in combat and loose clothing in social
situations, and both wear pendants of the Raven Queen.

\subsection{Ogden}\label{subsec:ogden}
\headeritem{Race}{Aasimar}
\headeritem{Voice}{Gaston}

  \begin{aloud}
  \label{description:ogden}
  Ogden looks like a fairytale prince had a bad run through the gladiator pit.
  His tan skin is practicably radiant, but covered with a patchwork of scars.
  He strong shoulders and broad frame collapse inward as he hunches.
  His lustrous blonde hair keeps a bounce even during combat, but is shaved down to stubble on
    the right with a jagged rune etched in.
  His eyes are as blue as the sky, but constantly twitch over the terrain, watching for, or perhaps
    searching for, a threat.

  Three parallel scars, an apparent claw mark, run down his neck and collarbone over over his heart.
  A tattoo of gills covers, or maybe accents, the scars.
  His brash attitude and tattoo combined to give him and, by relation,
    the adventurer band he fronts the nickname ``The Crazy Kuo-toa.''

  Ogden carries on his person enough steel to arm the entire band,
    and he carries very little beside.
  His glaive rarely leaves his hand.
  Two longswords cross on his back.
  A trio of sheathed daggers are strapped to either thigh.
  \end{aloud}

Wields a glaive, carries two longswords, and half a dozen daggers ``just in case.''

\subsubsection{Combat}
Use Gladiator stat block plus minor spellcasting, set CHA to 18, CR 5+
Can summon his glaive as an action, but typically has it at hand anyway.

\subsection{Goldie}\label{subsec:goldie}
\headeritem{Race}{Tiefling}
\headeritem{Voice}{Erika B. meets Erika W.}

\subsubsection{In combat}

Use Mage stat block.
Has cantrips Fire Bolt, Dancing Lights, Ray of Frost.
Add some Warlock spells.
In prepared battle, will wear Studded Leather Armor, set Cha 18, CR 6+
Can summon a warpick if melee combat is required.
