\section{Shomah and the Four Defiant}\label{sec:celadir}
Raven, Wrecker, Regent, Wrath.

\subsection{Shomah the Wrathful}
\headeritem{Creature type}{Neutral Good Female Human}

\subsection{The Worm, Celadir}
\headeritem{Name deformation}{Celadir the Wyrm}
\headeritem{Creature type}{Lawful Good Guardian Naga}

\subsection{The Raven}
\headeritem{Given name}{Meryl}
\headeritem{Also known as}{The Ragged Witch, The Raven's Message}
\headeritem{Creature type}{Chaotic Good Female Shadar-Kai}
\headeritem{Voice}{Molly from Dresden crossed with grandma Eileen}

\subsection{The Wrecker}
\headeritem{Given name}{Rekk'ur, commonly Rekk'}
\headeritem{Creature type}{Lawful Neutral Male Half-orc}

\subsection{The Raven}
\headeritem{Given name}{Sen-fa}
\headeritem{Creature type}{True Neutral Female Drow}


Use \href{https://i.imgur.com/HIvPzSj.jpg}{this} as the base stat block.
Convert fire to force.
Dex -> 20 for godlike status.
Resultant AC 19.
Sen-fa is under the effect of Jump and Longstrider as long as she is conscious.
Can cast Misty Step variant if it would "charge" into an attack.
Legendary Actions (3)
- Misty Step
- Shove attack
- Disarm attack

Sen-fa is a title, "Shadow Wrapped."
Think Shadow of Mordor with the ghost fading in and out, punching shit.
Describe as a blur vs 20/25 Perception check.
"Her blows are a blur, seemingly in two places at once."

[[Randomly here DM note:
Disarm variant is an attack contested by STR (Athletics) or DEX (Acro).
Skill check has advantage / disadvantage if there is a size difference.]]


