\section{The Landslide}

The Landslide were an squad in the Empress's Own auxiliary forces specializing in defense, escort,
  and extraction.
Consisting entirely of half- and non-human members, they were often isolated from the rest of the
  army.

\bigskip
\begin{center}
  \begin{tabular}{|l|l|}
    \hline
    \multicolumn{2}{|c|}{Landslide Members}\\
    \hline
    Role & Member \\
    \hline
    Leader & \hyperref[sec:beez]{John Smith} \\
    Scout & \hyperref[subsec:imrodel]{Imrodel} \\
    Sapper and Engineer & \hyperref[subsec:eagletamer]{Eagletamer} \\
    Fighter & \hyperref[subsec:fari]{Fari} \\
    Fighter & \hyperref[subsec:quinn]{Quinn} \\
    Fighter & \hyperref[subsec:alotel]{Alotel} \\
    \hline
  \end{tabular}
\end{center}


\subsection{Fari Drakegut}\label{subsec:fari}
Fari Drakegut is a 118 years old male hill dwarf soldier.
He has very long, wavy, auburn hair and blue eyes.
He has soft white skin.
He stands 117cm (3'10") tall and has a beefy build.
He has an edgy, disgusting face with a very long fu manchu moustache.
He smells of honey.
He quietly worships Chauntea, Goddess of agriculture, farmers, gardeners and summer. (Neutral Good)
He rarely thinks ahead.
He is extremely conceited.
He has lost many friend

\subsection{Imrodel Mithmirelen}\label{subsec:imrodel}
Imrodel Mithmirelen is a 268 years old female wood elf soldier.
She has long, straight, white hair and red eyes.
She has rough, ghostly, white skin.
She stands 124cm (4'0") tall and has a skinny build.
She has a sharp, pretty face.
She has 3 provocative piercings on her nose.
She openly worships Angharradh, Goddess of spring, fertility, planting, birth, defense, wisdom. (Chaotic Good)
She is very patient.
She is materialistic.
She occasionally uses terms from a different language as she speaks.
She can see an opening in any defense.
She always wears gloves.

\subsection{Eagletamer}\label{subsec:eagletamer}
Eagletamer is a 50 years old female goliath soldier.
She has a bald head with tribal tatoos and red eyes.
She has rough gray skin.
She stands 230cm (7'6") tall and has a beefy build.
She has a soft, very bland face.
She has an exceptional tribal tattoo on her back.
She openly worships Angharradh, Goddess of spring, fertility, planting, birth, defense, wisdom. (Chaotic Good)
She is constantly trying to outdo herself.
She is an example of modesty.
She never surrenders.
She is always sharing her wisdom.

\subsection{Quinn Hillless}\label{subsec:quinn}
Quinn Hillless is a 29 years old male half-elf soldier.
He has long, straight, red hair and blue eyes.
He has smooth brown skin.
He stands 167cm (5'5") tall and has a massive build.
He has a diamond-shaped, pretty face.
He has a large piercing on his lip.
He openly worships Moradin, God of dwarves, creation, smithing, protection, metalcraft, stonework. (Lawful Good)
He is always prepared.
He judges people by their actions, not their words.
He can see an opening in any defense.
He believes in destiny.

\subsection{Alotel Lithtaur}\label{subsec:alotel}
\headeritem{Pronounced}{Al oh tel, Lith to(w)er}
\headeritem{Alias}{Lilith}
\headeritem{Voice}{Say little, growl and threaten; alto, speak out the left of your mouth.}

Alotel Lithtaur is a 307 years old female high elf fighter.
She has long, curled, blond hair and green eyes.
She has rough copper skin.
She stands 134cm (5'4") tall and has a muscular build.
She has an sharp, beautiful face.
She smokes the pipe constantly.
A whirling tattoo marks her right hand.
She is missing the tip of her nose, from which a puckered scar runs down past her lip,
marring her otherwise beautiful face.
She perpetually scowls.
She compares everything to a fight.

\begin{aloud}
  \label{description:alotel}
  Alotel Lithtaur looks like a fine painting salvaged from a castle under siege.
  The high elf has the proud bearing, high cheekbones, and piercing eyes that so often define
    stereotypically attractive elven features.
  But a puckering scar runs from the missing tip of her nose, under her right eye, down to the
  corner of her lips, and around her jaw, leaving her in a perpetual sneer.
  A whirling tattoo marks her right hand and wrist, while old, poorly-healed burns adorn her left.
\end{aloud}

After acquiring her burns and Landslide is disbanded, Alotel deserts the Empress's Own and assumes
  the name Lilith.
Eventually, she finds her way across the country, moving from the western front to the eastern
  border and joining The Crazy Kuo-toa.
