\section{The Hellfish}
\headeritem{Also known as}{The Crazy Kuo-toa}

The Crazy Kuo-toa is an adventuring band that patrols the Eastern Wastes near the Bastion.
They track movement of the beast tribes, provide warning if it looks like they'll attack, and will
  help clear the area of more pressing threats, often with reinforcements from the Bastion.
Some few other bands do the same, but most come and go while the Kuo-toa endure.

\bigskip
\begin{center}
\begin{tabular}{|l|l|}
\hline
\multicolumn{2}{|c|}{Crazy Kuo-toa Members}\\
\hline
Role & Member \\
\hline
Frontman & \hyperref[subsec:ogden]{Ogden} \\
Leader & \hyperref[subsec:gluri]{Gluri} \\
Scout & \hyperref[subsec:buddyhawks]{Spacky} \\
Muscle & \hyperref[subsec:alotel]{Lilith} \\
Runner & \hyperref[subsec:garr]{Garr} \\
\hline
\end{tabular}
\end{center}

\subsection{Gluri Frosthand}\label{subsec:gluri}
\headeritem{Voice}{Gruff, curt, curses like a sailor.}
\headeritem{Statblock}{Duergar, minus sensitivity and innate magic}
% http://npcgenerator.azurewebsites.net/

Gluri Frosthand is a 200 years old male mountain dwarf ranger.
He has a bald head and black eyes.
He has rugged, sunburned, gray skin.
He stands 129cm (4'2") tall and has a muscular build.
He has a round, very ugly face with a medium goatee.
He is missing two fingers from his right hand.
(Frosthand, you see.)
He frequently asks questions, bordering Socratic in conversation.

\subsection{Garr Bolbec}\label{subsec:garr}
\headeritem{Voice}{Clipped, westerner's accent}

Garr Bolbec is a 47 years old male human messenger.
He has very long, curled, auburn hair and cyan eyes.
He has smooth, healthy, bronze skin.
He stands 172cm (5'7") tall and has a round build.
He has an pleasant, round face with a gigantic, braided beard.
He is branded on his left hand, and will never speak of its origin.
He is paranoid.
He knows all the best ways to torture someone.
He is a perfectionist.
